Unifying intra- and inter-specific variation in tropical tree mortality

### 2017-12-01 ms/manuscript.Rnw
Clarifying Fig 1C

\begin{figure}[!hb]
\centering
\includegraphics{figures/fig1.pdf}
\caption{Outline of methodology.
A) Our data consist of repeat measures of stem diameter ($D$) and status ($S$, alive or dead) for individual trees at specific census dates ($t_1$, $t_2$, $t_3$).
B) We consider three alternative hazard functions: 1) a baseline hazard, 2) a growth-dependent hazard; and 3) a function that combines both baseline and growth-dependent hazards. The parameters of the models are biologically interpretable: $\alpha$ defines the instantaneous mortality rate at low growth rate; $\beta$ reflects the sensitivity of mortality rate to changes in growth rate; and $\gamma$ is the asymptote, or baseline hazard. Combined $\alpha$ and $\beta$ capture growth-dependent mortality, while $\gamma$ captures growth-independent mortality (e.g. windfall, fire) that kill a plant, irrespective of its growth rate. For each model form, we consider two alternative predictors of growth, $X$ (basal area and stem diameter growth), as well as allowing for species-level effects on the parameters $\alpha$, $\beta$ and $\gamma$.
C) Predictions for plant survival and death are compared to observed outcomes. Incorrect predictions are penalised via the log-loss function.
D) The predictive skill of alternative models is evaluated via 10-fold cross validation. The entire dataset is split into 10 folds ($F_1$, ..., $F_{10}$). Alternative models were fit 10 times ($M_1$, ..., $M_{10}$), using different combinations of testing and training data. We then average the estimated log loss for each of these 10 model fits.}
\label{fig1}
\end{figure}

>>>>

\begin{figure}[!hb]
\centering
\includegraphics{figures/fig1.pdf}
\caption{Outline of methodology.
A) Our data consist of repeat measures of stem diameter ($D$) and status ($S$, 0 = alive or 1 = dead) for individual trees at specific census dates ($t_1$, $t_2$, $t_3$).
B) We consider three alternative hazard functions: 1) a baseline hazard, 2) a growth-dependent hazard; and 3) a function that combines both baseline and growth-dependent hazards. The parameters of the models are biologically interpretable: $\alpha$ defines the instantaneous mortality rate at low growth rate; $\beta$ reflects the sensitivity of mortality rate to changes in growth rate; and $\gamma$ is the asymptote, or baseline hazard. Combined $\alpha$ and $\beta$ capture growth-dependent mortality, while $\gamma$ captures growth-independent mortality (e.g. windfall, fire) that kill a plant, irrespective of its growth rate. For each model form, we consider two alternative predictors of growth, $X$ (basal area and stem diameter growth), as well as allowing for species-level effects on the parameters $\alpha$, $\beta$ and $\gamma$.
C) Each model's skill in predicting observed outcomes ($S$) is quantified via the log-loss function (eq. \ref{eq:logloss}).
D) The predictive skill of alternative models is evaluated via 10-fold cross validation. The entire dataset is split into 10 folds ($F_1$, ..., $F_{10}$). Alternative models were fit 10 times ($M_1$, ..., $M_{10}$), using different combinations of testing and training data. We then average the estimated log loss for each of these 10 model fits.}
\label{fig1}
\end{figure}
